---
title: "CV"
author: "dr. Aldilas Achmad Nursetyo, M.Sc."
output:
  pdf_document:
    latex_engine: pdflatex
    template: svm-latex-cv.tex
  html_document:
    df_print: paged
geometry: margin=1in
jobtitle: Researcher, Center for Health Policy & Management, Universitas Gadjah Mada
fontawesome: yes
phone: +62 813 9169 9700
email: mail.aldilas@gmail.com
web: aldeetropolis.github.io
updated: no
keywords: R Markdown, academic CV, template
fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 11pt
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Summary of Experience

Since 2017, Aldilas has been actively involved in contribute and developing at national and regional level, either academically or direct consultancy. He has experience in developing monitoring and evaluation system in National Family Planning Coordinating Agency (BKKBN) and strengthening national disease surveillance system, especially for early warning and response system (EWARS). He also experienced in research methodology, either quantitative or qualitative methodology, while demonstrating excelence scientific writing and publication experience.

# Education

*Taipei Medical University*, M.Sc. Biomedical Informatics \hfill 2019

*Universitas Muhammadiyah Yogyakarta*, M.D. \hfill 2015

*Universitas Muhammadiyah Yogyakarta*, Bachelor of Medicine \hfill 2012

# Projects

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(kableExtra)
projects <- read_xlsx("projects.xlsx")
knitr::kable(projects, "latex", booktabs = TRUE, longtable = TRUE) %>%
  column_spec(1, width = "1cm") %>% 
  column_spec(2, width = "5cm") %>% 
  column_spec(3, width = "10cm") %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header", "striped"))
```

# Publication

```{r echo=FALSE}
bib <- read.csv("citations.csv") %>% select(c(2:3, "Year")) %>% rename("Publication Title" = 1, "Publisher" = 2) %>% arrange(-Year)
knitr::kable(bib, "latex", booktabs = TRUE, longtable = TRUE) %>% 
  column_spec(1, width = "10cm") %>% 
  column_spec(2, width = "5cm") %>%
  column_spec(3, width = "1cm") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header", "striped"))
```
